\documentclass[../../thesis.tex]{subfiles}
\begin{document}
This thesis represents the culmination of my five-year journey studying mathematics at NTNU in Trondheim. I am deeply grateful to my supervisor, Rune Haugseng, who not only introduced me to the captivating world of algebraic topology and $\infty$-categories but also provided invaluable guidance throughout the process of writing this thesis.
Maybe most importantly, I thank him for devoting so much of his time to help me out when I'm stuck and answering all my questions (even though I frequently ended up asking the same questions again and again).


I want to thank everyone from Lesesal 395-B for constant moral support, collective procrastination, and sharing a beer during late-night proofreading sessions (which, admittedly, might have introduced a few new errors as well).
Special mentions go out to Tallak for enthusiastically calculating fiber products with me and to Thomas for proofreading.
Additionally, I would like to thank the mathematical community for making their books, papers and notes freely accessible to the world.


While this thesis is the conclusion of my five years in Trondheim, I have learned far more mathematics than I have managed to squeeze in here, and in my time as a student, I have done far more than just learn mathematics.
I thank NCF for helping me keep somewhat in shape and for providing a welcome break between exam preps.


On a personal level, many friends and family deserve a thank you.
Clearly, I must thank my parents, because without them this thesis would not exist.\footnote{The proof is trivial and left as an exercise to the reader.}
I would also like to extend some extra gratification towards my roommates Johan and Sander and to Sophia for making these past years as a student much better than I dared hope for.
\end{document}
%This thesis represents the culmination of my five-year journey studying mathematics at NTNU in Trondheim. I am deeply grateful to my supervisor, Rune Haugseng, who not only introduced me to the captivating world of algebraic topology and $\infty$-categories but also provided invaluable guidance throughout the process of writing this thesis. His unwavering support, endless patience in addressing my repeated questions, and generous allocation of time have been instrumental to its completion.


%I would like to express my sincere appreciation to the entire group at Lesesal 395-B. Their constant moral support, collective indulgence in procrastination, and shared moments over a beer during late-night proofreading sessions (which, admittedly, might have introduced a few new errors) have made this journey all the more enjoyable. I extend special thanks to Tallak for enthusiastically joining me in calculating fiber products and to Thomas for his invaluable assistance in proofreading.


%Additionally, I would like to acknowledge the authors and the wider mathematical community for providing freely accessible resources. Your contributions have been instrumental in my research and understanding of the subject matter.


%Although this thesis marks the end of my time in Trondheim, it is important to note that I have acquired a wealth of mathematical knowledge beyond what is presented here. Moreover, my experience as a student encompassed more than just learning mathematics. On a personal level, I am grateful to my friends and family who have supported me throughout this journey. I would like to extend special gratitude to my roommates, Johan and Sander, as well as to Sophia, for making these past years as a student far more rewarding than I could have ever imagined.