\documentclass[../../thesis.tex]{subfiles}
\begin{document}
The main goal of this thesis is to understand and reproduce Jacob Lurie's version of Verdier duality for sheaves valued in stable $\infty$-categories.
The first four chapters in this thesis are dedicated to building the framework and gathering the tools we need to prove the theorem.


In chapter \ref{infcatchap}, we introduce simplicial sets and $\infty$-categories.
There are many excellent introductions to the world of $\infty$-categories and beyond.
We mostly follow \cite{kerodon} and \cite{Rezk}.


In chapter \ref{limscolims}, we continue our introduction to $\infty$-categories and introduce the machinery required to define $\infty$-categorical versions of limits and colimits.
We also introduce the notion of a cofinal functor and present a result that greatly simplifies the calculation of limits and colimits of certain functors.
Finally, we define stable $\infty$-categories and introduce some examples and valuable results.


In chapter \ref{kanchap}, we first recall the definitions of Kan extensions in ordinary category theory and present some selected results and examples.
Kan extensions are ubiquitous concept in category theory, and their properties will be central in proving Verdier duality.


In chapter \ref{sheavescap}, we introduce sheaves on locally compact Hausdorff spaces and their compact counterpart $\K$-sheaves.
The main goal of this chapter is to prove Theorem \ref{7.3.4.9} which says that for an $\infty$-category $\C$ and a locally compact Hausdorff space $X$ there is a categorical equivalence between the $\infty$-category $\Shv(X;\C)$ of $\C$-valued sheaves on $X$ and the $\infty$-category $\Shv_{\K}(X;\C)$ of $\C$-valued $\K$-sheaves.
We start the chapter by recalling the definition of sheaves valued in $1$-categories and give a short recollection of the history of sheaf theory.

In chapter \ref{verdiercap}, we prove Theorem \ref{VerdierDuality}: Verdier duality.
The theorem says that for a stable $\infty$-category and a locally compact Hausdorff space $X$ there is an equivalence between the $\infty$-category $\Shv(X;\C)$ of $\C$-valued sheaves on $X$ and the $\infty$-category $\Shv(X;\C^{op})^{op}$ of $\C$-valued cosheaves on $X$.
Using Theorem \ref{7.3.4.9}, we restate the theorem as an equivalence between $\infty$-categories of $\K$-sheaves instead, and while this is a crucial part of the proof, it also clarifies the connection to the classical Verdier duality.
We start the chapter by recalling classical Verdier duality and its relation to Poincaré duality.
\end{document}