\documentclass[../thesis.tex]{subfiles}

% Seperate preamble for this subfile. This preamble is loaded last, so it may be used to override various functions.

\begin{document}
    \section{When I girlbossed to close to the sun}

    So, it all started when I was girlbossing my way through high school. I was around 17-18 at the time. I heard that boys had difficulties with girls who post selfies in suggestive poses… I just wanted to show the world that my legs were better than theirs. I did it for a year and got a lot of attention from it. I guess because I looked good in my selfies. But then I got tired of it. I just stopped posting them.

    At this time I discovered a newfound attention directed towards me. Everyone wanted to see me – my godlike legs. I had legs for days and everyone new, even the teachers. A true girlboss never pass on a business opportunity like this, so the boys got what they wanted for some quid pro quo.

    At that time, I was also failing chemistry. I was sweating and crying in my chem class. But I didn’t care because I had my legs and my girls. But 2 weeks before the end of school I decided that I hated my life and that I was going kill myself. I wrote a long letter to my parents, told them how much I loved them and how sorry I was. At this point I was a mess.

    Mr. Wilson, my chemistry and homeroom teacher was notified about my actions. He knew that I was going to kill myself if I didn't pass chemistry. Mr. Wilson was a man of culture, and he appreciated a good pair of legs when he saw one. He knew of my quid pro quo, and let's just say that I didn't just pass chemistry, I got an A+.

    Someone may find it strange that an average student over night suddenly becomes an A-student. This is exactly what happened. I didn't just girlboss myself an A in chemistry, I rather fixed my whole report. Hannah was so jealous of my accomplishment that she started to spread rumors, but only I knew that it was actually true. I was outed at graduation for doing favors for my teachers. The only problem was that they started to talk among themselves, and so they all knew the truth.

    I ran off and never look back. 

    A year has passed.

    I am at work.

    I am the manager. How did I become the manager? Well you can ask yourself this question, but we all know the answers. 

    This is just the start of my story. I will keep publishing until the end of this year.

    - Sarah
\end{document}